\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{url}

\newenvironment{tscode}
{\begin{list}{}{\setlength{\leftmargin}{1em}}\item\scriptsize\bfseries}
{\end{list}}

\title{Tecellate: A Distributed Environment for Ad Hoc Wireless Network Simulations}
\author{
        Steve Johnson (srj15@case.edu)\\
        Case Western Reserve University\\
        \and Tim Henderson (tah35@case.edu)\\
        Case Western Reserve University
}
\date{\today}

\begin{document}
\doublespacing
\maketitle

% \begin{multicols}{2}

\begin{abstract}
    Tecellate is a simulation in which autonomous agents can move in a grid and communicate using
    semi-realistic radio signals. The simulation itself can be distributed over multiple machines to
    allow for very large simulations. The system allows researchers to test various wireless network
    protocols and algorithms under arbitrarily harsh conditions.
    
    The usefulness of the simulation was tested using an approximated IP stack. Our initial results
    show that the simulation produces useful information, though more work is required to improve
    its accuracy and suitability for research.
\end{abstract}

\section{Introduction}

Computer network modeling and simulation has become an important tool in the arsenal of any computer
networks researcher. It has only become more important as increasingly research into mobile
and autonomous devices matures. Large scale simulations of thousands to hundreds of thousands of
devices become increasingly crucial to validate techniques without having to spend thousands of
dollars on costly equipment. To support such simulations we present Tecellate, a horizontally
scalable distributed network simulator.

Tecellate simulates the physical layer of the network. All \textbf{agents} (actors in the
simulation) have a ``radio'' to send and receive byte strings. To approximate the real world, these
byte strings may be probabilistically corrupted as a function of distance and interference. To
provide reliable communication between arbitrary agents, users must implement the link, IP, and
transport layers. As a resource to users wishing to model the traditional TCP/IP stack the authors
provide a partial implementation up to the IP layer.\footnote{
  We hope to expand this implementation to include the TCP and UDP transport layers as well.
}

In the physical world, devices move around with purpose and transmit with purpose. We assert that
the same should be true in a simulation. However, modeling the purpose of actual people is not
possible. Therefore, the simulation gives the agents an alternative purpose: to stay alive. Each
agent has to ``eat'' in order to survive. Each turn, each agent may eat a unit of food if its
current location contains food. If it runs out of food, it dies. The goal of the agents is to stay
alive as long as possible. Thus, it must find sources of food within the simulation. This game-like
element provides the agents with goals and a purpose for communication.

As wireless networks become more widespread, the number of participants in a given network will
grow. Simulations that are not scalable may become too slow to simulate important test cases. For
this reason, Tecellate is designed to scale horizontally across many machines.

By modeling the communication at the physical layer and adding game-like elements to our simulation,
we hope to provide an interesting test bed for networking and AI algorithms. The game-like element
in our simulation will help ensure the agents move around purposefully in the simulation grid. The
physical layer simulation ensures that the communication problems which must be overcome for
reliable communication are similar to real world problems. The inherent scalability of the system
should allow simulation of arbitrarily large scenarios. While, we do not think our simulation
approach would be the final word in networks simulation, it should provide a useful platform for
experimentation.

\input{litsurvey}

\input{world}

\input{architecture}

\input{validation}

\input{conclusion}

\nocite{*}
\bibliographystyle{acm}
\bibliography{bibliography}

\end{document}
